Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
conclusion style correction

\paragraph{Future work}
There are multiple directions for future work on this topic.
The system we presented would become more useful in an interactive setting where users can easily receive and provide feedback.
Moreover, the system can be adapted to produce less redundant constraints through the use of heuristic filtering.

Currently, the system only learns single constraints, however, extending this approach to nested constraints would allow more expressive concepts to be learned.
This shift would bring the approach in line with programming by example.

>>>>

\paragraph{Future work}
There are multiple directions for future work on this topic.
The system would be easier to use in an interactive setting where users can easily receive and provide feedback.
Moreover, the system can be adapted to produce less redundant constraints through the use of heuristic filtering.

Currently, the system only learns single constraints, however, extending it to nested constraints would allow more expressive concepts to be learned.
This shift would bring the approach in line with programming by example.
